Basic MODIS preparation in GRASS GIS

### 2011-01-04 tutorials/grass_modis/article_GIPE.tex
Updated MCD43B3/B2 Quality processing info
git-svn-id: https://svn.osgeo.org/grass/grass-promo@44874 15284696-431f-4ddb-bdfa-cd5b030d7da7

>>>>

When Dealing with BRDF-Corrected Albedo product (i.e. MCD43B3), a complement quality product should be downloaded, MCD43B2. This product has two Sub-Datasets (SDS) that are not bit-packed, therefore can be read directly but r.mapcalc. These SDS are \textit{BRDF\_Albedo\_Quality} and \textit{Snow\_BRDF\_Albedo}.

\begin{smallverbatim}
BRDF_Albedo_Quality
-------------------
 Value 0: Processed, good quality \
    (full BRDF inversion) 
 Value 1: Processed, see other QA \
    (magnitude BRDF inversions)
 Value 255: Fill Value
\end{smallverbatim}

\begin{smallverbatim}
Snow_BRDF_Albedo
----------------
 Value 0: Snow-free albedo retrieved  
 Value 1: Snow albedo retrieved 
 Value 255: Fill Value
\end{smallverbatim}
